Correlating Scanning Ion Conductance and Super-Resolved Fluorescence Microscopy

### 2020-10-18 sections/srfm.tex
reworked

This led to the invention of the confocal microscope
\cite{Heimstaedt1911,Minsky1988}. The beam path of a confocal microscope is
shown in Fig.~\ref{fig:FM-setups}b. Here, the excitation light (green solid
shape) is focused onto the sample by the objective lens and only the
fluorophores within the resulting diffraction limited spot are excited. Thus, the
wavelength which determines the resolution of a confocal microscope is the
excitation wavelength $\lambda_\text{ex}$.  In contrast to the wide-field
microscope, the emission of the fluorophores is focused onto a pinhole which
is located in front of a single detector (left inset in
Fig.~\ref{fig:FM-setups}b). Since this setup does not allow imaging the entire
sample at once, the sample has to be scanned with respect to the excitation
light beam and the image is collected pixel by
pixel. Fig.~\ref{fig:FM-setups}c illustrates the major effect of the pinhole:
Emission from out-of-focus planes (dotted and dashed lines) is blocked by the
pinhole since it is located in the same focal plane as the sample (thus the
name \emph{confocal}).

@@

\begin{figure}
  \centering
  \includegraphics{gr/intro/localisation-mic}
  \caption{}
  \label{fig:lm}
\end{figure}

The principle of these methods is illustrated in Fig.~\ref{fig:lm}. Initially,
all fluorophores within the sample are inactivated (``off''-state, grey dots
in Fig.~\ref{fig:lm}a). Next, light suitable to switch the fluorophores (cyan
background, Fig.~\ref{fig:lm}b) from the inactivated to the activated (``on'')
state (white dots) is applied. The intensity of the activation light is
selected such that only a small subset of the inactivated molecules is
activated, at maximum one molecule per area of the diffraction limited
spot. The activated molecules are excited (green background, yellow dots) and
their emission is recorded. The excitation light is applied as long as all
excited molecules have bleached (black dots). The series of activation,
excitation and read-out is repeated until all fluorophores have been excited
and bleached, which results in a set of images containing diffraction limited
emission spots of all fluorophores in the sample.

@@

In summary, this directly yields a recording of the fluorophores with a
resolution beyond the diffraction limit (Fig.~\ref{fig:STED-principle}d). The
resolution provided by STED microscopy depends on the intensity $I$ of the
depletion beam and is given by
\begin{equation}
  d_\text{min, STED} = \frac\lambda{2\mathrm{NA}\sqrt{I/I_\text{sat}}}\text,
  \label{eq:resolution-STED}
\end{equation}
which is a modification of Abbe's original equation
(eq.~\eqref{eq:diffraction-limit}). Here, $I_\text{sat}$ is the intensity
required to induce stimulated emission in half of the fluorophores.

The best resolution (approximately 2\,nm) obtained by STED microscopy has
been recorded on samples containing fluorescent color centers in diamond
crystal \cite{Wildanger2012}. Note that, by applying a depletion beam of a
different shape, STED microscopy allows to improve the resolution along the
optical axis \cite{Harke2008, Wildanger2009}. A large number of reviews articles exist
which summarize the use of STED (or in general, RESOLFT) microscopy in different
fields in the life sciences, much too much to be listed here. We would like to
refer the reader to exhaustive reviews, which, besides
reviewing various applications, detail technical aspects of STED microscopy
\cite{Turkowyd2016,Blom2017} as well as to a review which contains some
anecdotal sections on how STED was developed \cite{Sahl2019}.

>>>>

This led to the invention of the confocal microscope
\cite{Heimstaedt1911,Minsky1988}. The beam path of a confocal microscope is
shown in Fig.~\ref{fig:FM-setups}b. Here, the excitation light (green solid
shape) is focused onto the sample by the objective lens and only the
fluorophores within the resulting diffraction limited spot are excited. Thus, the
wavelength which determines the resolution of a confocal microscope is the
excitation wavelength $\lambda_\text{ex}$.  In contrast to the wide-field
microscope, the emission of the fluorophores is focused onto a pinhole which
is located in front of a single detector (left inset in
Fig.~\ref{fig:FM-setups}b). Since this setup does not allow imaging the entire
sample at once, the sample has to be scanned with respect to the excitation
light beam and the image is collected pixel by
pixel. Figure~\ref{fig:FM-setups}c illustrates the major effect of the pinhole:
Emission from out-of-focus planes (dotted and dashed lines) is blocked by the
pinhole since it is located in the same focal plane as the sample (thus the
name \emph{confocal}).

@@

\begin{figure}
  \centering
  \includegraphics{gr/intro/localisation-mic}
  \caption{%
    \textbf{Principle of PALM.}
    \textbf{a:} Initially, all fluorophores are in the inactivated state (grey
    dots).
    \textbf{b:} A small subset of the fluorophores is activated (cyan
    background, white dots) and subsequently excited (green background, yellow
    dots) until the fluorophores bleach (black dots). The emission of the
    fluorophores is recorded. This series is repeated until all fluorophores
    have emitted.
    \textbf{c:} The positions of the fluorophores in the recordings are
    determined and plotted as a Gaussian distribution with a standard
    deviation equal to the uncertainty of the localisation and the single
    images are combined to a single image with improved resolution.
  }
  \label{fig:lm}
\end{figure}

As an example, the principle of PALM is illustrated in Fig.~\ref{fig:lm}. Initially,
all fluorophores within the sample are inactivated (``off''-state, grey dots
in Fig.~\ref{fig:lm}a). Next, light suitable to switch the fluorophores (cyan
background, Fig.~\ref{fig:lm}b) from the inactivated to the activated (``on'')
state (white dots) is applied. The intensity of the activation light is
selected such that only a small subset of the inactivated molecules is
activated, at maximum one molecule per area of the diffraction limited
spot. The activated molecules are excited (green background, yellow dots) and
their emission is recorded. The excitation light is applied as long as all
excited molecules have bleached (black dots). The series of activation,
excitation and read-out is repeated until all fluorophores have been excited
and bleached, which results in a set of images containing diffraction limited
emission spots of all fluorophores in the sample.

@@

In summary, this directly yields a recording of the fluorophores with a
resolution beyond the diffraction limit (Fig.~\ref{fig:STED-principle}d). The
resolution provided by STED microscopy depends on the intensity $I$ of the
depletion beam and is given by
\begin{equation}
  d_\text{min, STED} = \frac\lambda{2\mathrm{NA}\sqrt{I/I_\text{sat}}}\text,
  \label{eq:resolution-STED}
\end{equation}
which is a modification of Abbe's original equation
(Eq.~\ref{eq:diffraction-limit}). Here, $I_\text{sat}$ is the intensity
required to induce stimulated emission in half of the fluorophores. The best resolution (approximately 2\,nm) obtained by STED microscopy has
been recorded on samples containing fluorescent color centers in diamond
crystal \cite{Wildanger2012}.

Note that, by applying a depletion beam of a
different shape, STED microscopy allows to improve the resolution along the
optical axis \cite{Harke2008, Wildanger2009}. A large number of reviews articles exist
which summarize the use of STED (or in general, RESOLFT) microscopy in different
fields in the life sciences, much too much to be listed here. We would like to
refer the reader to exhaustive reviews, which, besides
reviewing various applications, detail technical aspects of STED microscopy
\cite{Turkowyd2016,Blom2017} as well as to a review which contains some
anecdotal sections on how STED was developed \cite{Sahl2019}.
